A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-08 paper.tex
minor edits

\subsection*{Applications to Quantization and a Relationship to Factorization algebras}
%\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re

@@

We explain how to define the BV bracket in our context.  
First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
\[
X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
For $n > 1$, define
\begin{align*}
\Psi_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(\Psi(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
\end{proof}

@@

\begin{proof}
Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

@@

\subsubsection{Generalized Hodge Theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\begin{definition}
The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2$-graded bundle:
\[
F_{\rm gauge} = \Omega^1(V_\RR; \fg) \oplus \Gamma(V_\RR; \Pi \Sigma \otimes \fg) \oplus \Omega^0(V_\RR; \fg[1])
\]
whose sections we denote by $(A, \lambda, c)$.  
The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d : \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
\[
\begin{array}{ccccccc}
[-,-] & : & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
\end{array}
\]
defined by $[c, A + \lambda + c'] = [c, A] + [c, \lambda] + [c,c']$.
The BRST action is defined by
\[
S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).
\]
\end{definition}

@@

We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]

@@

\begin{theorem} 
The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} 
The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} 
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. %Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}

@@

\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}

>>>>

@@

We explain how to define the BV bracket in our context.  
First note that there is a linear map
\[
\d_{\mr{dR}} \colon \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i \colon \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega \colon {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
\[
X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
For $n > 1$, define
\begin{align*}
\Psi_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(\Psi(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
\end{proof}

@@

\begin{proof}
Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

@@

\subsubsection{Generalized Hodge Theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\begin{definition}
The BRST theory for classical supersymmetric Yang-Mills theory has underlying $\ZZ \times \ZZ/2$-graded bundle:
\[
F_{\rm gauge} = \Omega^1(V_\RR; \fg) \oplus \Gamma(V_\RR; \Pi \Sigma \otimes \fg) \oplus \Omega^0(V_\RR; \fg[1])
\]
whose sections we denote by $(A, \lambda, c)$.  
The dg Lie structure on $F_{\rm gauge}[-1]$ has differential given by the de Rham differential $\d :\colon \Omega^0(V_{\RR} ; \fg) \to \Omega^1(V_{\RR} ; \fg)$ and bracket
\[
\begin{array}{ccccccc}
[-,-] & \colon & \Omega^0(V_{\RR} ; \fg) \otimes \left(\Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_{\RR} ; \fg) \right) & \to & \Omega^1(V_{\RR} ; \fg) \oplus \Gamma(V_\RR ; \Sigma \otimes \fg) \oplus \Omega^0(V_\RR ; \fg)
\end{array}
\]
defined by $[c, A + \lambda + c'] = [c, A] + [c, \lambda] + [c,c']$.
The BRST action is defined by
\[
S_{\mr{BRST}}(A, \lambda) = \int_{V_\RR}\dvol \left( -\frac{1}{4} (F_A, F_A) + \frac{1}{2}(\lambda, \sd \d_A \lambda)\right).
\]
\end{definition}

@@

We use the same twisting homomorphism $\phi \colon \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha \colon U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]

@@

\begin{theorem}  \label{3d_8_minimal_twist_thm}
The minimal twist of 3d $\cN=8$ super Yang--Mills on $M=\CC\times \RR$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Dol}})$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} \label{3d_8_A_twist_thm}
The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} \label{3d_8_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. %Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}

@@
